The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-04 outputs/paper/paper.Rmd
discussion writing

# Introduction
Trust is a big matter in this world. Especially when you need assistance in fields that you are unfamiliar with, trust is the best thing that you can rely on. For instance, if you need a lawyer, the best thing that you can do is to trust your lawyer, and be 100% honest. In medical field, trust is directly related to your life. We are certain that you have observed that many people have been refusing to get COVID-19 vaccines. Then, we started to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that safety are proved and guaranteed such as BCG vaccine for preventing tuberculosis. It is true that we no longer have doubts against them. However, if you move sight to developing country in 1980~1990s, situation would certainly different because of lack of well constructed healthcare system or other reasons. This curiosity triggered us to start this research.

@@

## Weaknesses

## Next steps for future

>>>>

# Introduction
Trust is a very important but also a big issue in this world. Especially when you need assistance in fields that you are unfamiliar with and require help from others, trust is the best thing that you can rely on. For instance, if you need a legal advice, the best thing that you can do is to trust your lawyer, and be 100% honest. In medical field, trust is directly related to your life. We are certain that you have observed that many people have been refusing to get COVID-19 vaccines. Then, we started to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that safety are proved and guaranteed such as BCG vaccine for preventing tuberculosis. It is true that we no longer have doubts against them. However, if you move sight to developing country in 1980~1990s, situation would certainly different because of lack of well constructed healthcare system or other reasons. This curiosity triggered us to start this research.

@@

## Weaknesses 
Dataset does not have wide variety of information, more categories such as more variety on religion, additional information such as household income, number of hospitals in each region, and how easy to access to those hospitals, especially for rural areas, with worse public transportation.
## Next steps for future
